\vfill A Testing Framework for Web Application

### 2014-01-29 Paper/paper.tex
Update to bib, Unit Testing expansion with example, javascript listing setup

% Two Column Format
\documentclass[11pt]{article}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{multicol, caption}
\usepackage{verbatim}

@@

\subsection{Why Testing is Important}
I'm consistently surprised by how few people take testing seriously when it comes to non-trivial applications.

\subsubsection{What is testing?}
IEEE defines software testing as ``the process of analyzing a software item to detect the differences between existing and required conditions (that is, bugs) and to evaluate the features of a software item.'' \cite{TestingDefinition}
Although there are a number of different types of tests and testing concepts, we will focus on Unit Testing and Continuous Integration.

\paragraph{Unit Testing}
Unit testing is the testing of specific functions and functionality. Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What's important to remember in regards to unit testing is that it tests just one portion of the code or system rather than interactions between modules or the entire system.

\paragraph{Continuous Integration}
Continuous integration, in the context of testing, is the term for a piece of software or service that continually runs tests on your code as you develop. The purpose of this is to make sure that new code is not breaking old tests and that new code is passing any tests you've written for it.
One of the most important pieces of this is that it is automatic. There should be no need for a developer to do anything besides ``turn it on'' and start coding. As soon as a tool requires more than one or two interactions, it becomes much more of a nuisance and less of a helper.

@@

>>>>

% Two Column Format
\documentclass[11pt]{article}
%this allows us to specify sections to be single or multi column so that things like title page and table of contents are single column
\usepackage{multicol, caption}
\usepackage{verbatim}
\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

\lstset{frame=tb,
  language=JavaScript,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
  tabsize=3
}

@@

\subsection{What is testing?}
IEEE defines software testing as ``the dynamic verification of the behavior of a program on a finite set of test cases, suitably selected from the usually infinite executions domain, against the expected behavior.'' \cite{TestingDefinition} Put a bit more simply, software testing is the process of making sure the program does what it is supposed to.
There are a number of different types of tests and testing concept, we will just focus on Unit Testing and Continuous Integration.

\subsubsection{Unit Testing}
Unit testing is the testing of specific functions and functionality. Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

Here's a very brief example:
\begin{lstlisting}
// Terribly useless code whose purpose is to eventually calculate a magic number
function addTwo (numToAddTo) {
	return numToAddTo + 2;
}

function twoTimes (numToMultiply) {
	var sum = 0;

	for (var i = 0; i < numToMultiply; i++) {
		sum = addTwo(sum);
	}

	return sum;
}

.... // More functions

function calculateMagicNumberPartOne (startingNum) {
	var foo = 3 + addTwo(startingNum);

	return twoTimes(foo);
}

... // More functions

function calculateMagicNumber (startingNum) {
	var numSoFar = calculateMagicNumberPartOne(startingNum);

	numSoFar = calculateMagicNumberPartTwo(numSoFar);
	numSoFar = calculateMagicNumberPartThree(numSoFar);
	... // More calculateMagicNumberPart(s)

	return numSoFar;
}

function testAddTwo () ... // Unit Test
function testTwoTimes () ... // Unit Test
function testCalculateMagicNumberPartOne () ... // Still a Unit Test, just a whole module of functionality

function testCalculateMagicNumber () ... // NOT a Unit Test because it's testing the whole system
\end{lstlisting}

\subsubsection{Continuous Integration}
Continuous integration, in the context of testing, is the term for a piece of software or service that continually runs tests on your code as you develop. The purpose of this is to make sure that new code is not breaking old tests and that new code is passing any tests you've written for it.
One of the most important pieces of this is that it is automatic. There should be no need for a developer to do anything besides ``turn it on'' and start coding. As soon as a tool requires more than one or two interactions, it becomes much more of a nuisance and less of a helper.

@@

\subsubsection{Why Testing is Important}
I'm consistently surprised by how few people take testing seriously when it comes to non-trivial applications.
